### 2021-05-26 papers/thesis/full/ch3-disk-slices/disk-slices.tex
Fig sizes changed to be consistent and bigger.

\begin{figure}[t]
	\begin{subfigure}{0.32\textwidth}
	\includegraphics[scale=0.35]{sparsityoflaplacian-w11-diskslice-alpha=0p2-beta=0p8}
        \centering
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
	\includegraphics[scale=0.35]{sparsityofhelmholtz-diskslice-alpha=0p2-beta=0p8}
        \centering
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
	\includegraphics[scale=0.35]{sparsityofbiharmonic-diskslice-alpha=0p2-beta=0p8}
        \centering
	\end{subfigure}
    	\caption{"Spy" plots of (differential) operator matrices, showing their sparsity. Left: the Laplace operator $\laplacewiii$. Centre: the weighted variable coefficient Helmholtz operator $\laplacewiii + k^2 \: T^{(0,0,0)\to(1,1,1)} \: V({J_x^{(0,0,0)}}^\top, {J_y^{(0,0,0)}}^\top) \: T_W^{(1,1,1)\to(0,0,0)}$ for $v(x,y) = 1 - (3(x-1)^2 + 5y^2)$ and $k = 200$. Right: the biharmonic operator $\biharmonictwo$.}
        \label{fig:sparsity}
        \centering
\end{figure}

General linear partial differential operators with polynomial variable coefficients can be constructed by composing the sparse representations for partial derivatives, conversion between bases, and Jacobi operators. As a canonical example, we can obtain the matrix operator for the Laplacian \(\Delta\), that will take us from coefficients for expansion in the weighted space
\bseqn{
	\bigWiii(x,y) = \Wiii(x,y) \: \bighdopiii(x,y)
}
to coefficients in the non-weighted space $\bighdopiii(x,y)$. Note that this construction will ensure the imposition of the Dirichlet zero boundary conditions on $\Omega$. The matrix operator for the Laplacian we denote $\laplacewiii$ acting on the coefficients vector is then given by
\bseqn{
    \laplacewiii := D_x^{(0,0,0)} \: W_x^{(1,1,1)} + T^{(0,0,1)\to(1,1)} \: D_y^{(0,0,0)} \: T_W^{(1,1,0)\to(0,0,0)} \: W_y^{(1,1,1)}.
}
Importantly, this operator will have banded-block-banded structure, and hence will be sparse, as seen in Figure \ref{fig:sparsity}.

@@

% FIGURES
\begin{figure}[t]
	\begin{subfigure}{0.3\textwidth}
	\includegraphics[scale=0.3]{solution-poisson-diskslice-alpha=0p2-beta=0p8}
	\centering
	%\label{fig:solution-poisson}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
	\centering
	\includegraphics[scale=0.5]{solutionblocknorms-poisson-diskslice-alpha=0p2-beta=0p8-N=200}
        	%\label{fig:solutionblocknorms-poisson}
	\end{subfigure}
	\caption{Left: The computed solution to $\Delta u = f$ with zero boundary conditions with $f(x,y) = 1 + \text{erf}(5(1 - 10((x - 0.5)^2 + y^2)))$. Right: The norms of each block of the computed solution of the Poisson equation with the given right hand side functions. This demonstrates algebraic convergence with the rate dictated by the decay at the corners, with spectral convergence observed when the right-hand side vanishes to all orders.}
	\centering
	\label{fig:poisson}
\end{figure}

\begin{figure}[t]
	\begin{subfigure}{0.3\textwidth}
	\includegraphics[scale=0.3]{solution-exact-poisson-diskslice-alpha=0p2-beta=0p8-u=y3expx}
	\centering
	\end{subfigure}
	\begin{subfigure}{0.3\textwidth}
	\centering
	\includegraphics[scale=0.3]{solution-exact-poisson-diskslice-alpha=0p2-beta=0p8-u=y3expx-actual}
	\centering
	\end{subfigure}
	\begin{subfigure}{0.3\textwidth}
	\includegraphics[scale=0.3]{solution-exact-poisson-diskslice-alpha=0p2-beta=0p8-u=y3expx-compare}
	\centering
	\end{subfigure}
	\centering
	\caption{The computed solution to $\Delta u = f$ with zero boundary conditions compared with the exact solution $u(x,y) = \Wiii (x,y) y^3 \exp(x)$. Left: Computed. Centre: Exact. Right: Plot of the error (colourbar is shown to demonstrate magnitude of the error is of the order $10^{-17}$)}
	\centering
	\label{fig:poissonexact}
\end{figure}

\begin{figure}[t]
	\begin{subfigure}{0.3\textwidth}
	\centering
	\includegraphics[scale=0.3]{solution-helmholtz-diskslice-alpha=0p2-beta=0p8-k=100-n=300}
	%\label{fig:solution-helmholtz}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
	\includegraphics[scale=0.5]{solutionblocknorms-helmholtz-diskslice-alpha=0p2-beta=0p8-N=196-k=20}
	\centering
        	%\label{fig:solutionblocknorms-helmholtz}
	\end{subfigure}
	\caption{Left: The computed solution to $\Delta u + k^2 \: v \: u = f$ with zero boundary conditions with $f(x,y) = x(1-x^2-y^2)e^x$, $v(x,y) = 1 - (3(x-1)^2 + 5y^2)$ and $k = 100$. Right: The norms of each block of the computed solution of the Helmholtz equation with the given right hand side functions, with $k=20$ and $v(x,y) = 1 - (3(x-1)^2 + 5y^2)$.}
	\centering
	\label{fig:helmholtz}
\end{figure}

\begin{figure}[t]
	\begin{subfigure}{0.3\textwidth}
	\centering
	\includegraphics[scale=0.3]{solution-biharmonic-diskslice-alpha=0p2-beta=0p8}
	%\label{fig:solution-biharmonic}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
	\includegraphics[scale=0.5]{solutionblocknorms-biharmonic-diskslice-alpha=0p2-beta=0p8-N=200}
	\centering
        	%\label{fig:solutionblocknorms-biharmonic}
	\end{subfigure}
	\caption{Left: The computed solution to $\Delta^2 u = f$ with zero Dirichlet and Neumann boundary conditions with $f(x,y) = 1 + \text{erf}(5(1 - 10((x - 0.5)^2 + y^2)))$. Right: The norms of each block of the computed solution of the biharmonic equation with the given right hand side functions.}
	\centering
	\label{fig:biharmonic}
\end{figure}
% END FIGURES

@@

\subsection{End-Disk-Slice}\label{Appendix:HalfDisk}

@@

In Figure \ref{fig:appendixfigs} we see the solution to the Poisson equation with zero boundary conditions in the half-disk $\Omega$ with $(\alpha,\beta) := (0,1)$.

\subsection{Trapeziums}\label{Appendix:Trapezium}

@@

In Figure \ref{fig:appendixfigs} we see the solution to the Helmholtz equation with zero boundary conditions in the trapezium $\Omega$ with $\xi := \half$.

@@

%%
%\section{Conclusions}
%
%
%We have shown that bivariate orthogonal polynomials can lead to sparse discretizations of general linear PDEs on specific domains whose boundary is specified by an algebraic curve---notably here the disk-slice---with Dirichlet boundary conditions.  This work extends  the triangle case \cite{beuchler2006new,li2010optimal,olver2019triangle} to non-classical geometries, and forms a building block in developing an $hp-$finite element method to solve PDEs on other polygonal domains by using suitably shaped elements, for example, by dividing the disk into disk slice elements. 
%%A further extension is to develop similar relationships for 3D domains such as the half-sphere surface. With this, we can obtain a family of OPs on the half-sphere, with sparse relations, and construct sparse spectral methods for surface PDEs on half-spheres. 
%This work serves as a stepping stone to constructing similar methods to solve partial differential equations on 3D sub-domains of the sphere, such as spherical caps and spherical triangles. In particular, orthogonal polynomials (OPs) in cartesian coordinates ($x$, $y$, and $z$) on a half-sphere can be represented using two families of OPs on the half-disk, see \cite[Theorem 3.1]{olver2018orthogonal} for a similar construction of OPs on an arc in 2D, and it is clear from the construction in this paper that discretizations of spherical gradients and Laplacian's are sparse on half-spheres and other suitable sub-components of the sphere. The resulting sparsity in high-polynomial degree discretizations presents an attractive alternative to methods based on bijective mappings (e.g., \cite{DGShallowWater,FEMShallowWater,boyd2005sphere}). Constructing these sparse spectral methods for surface PDEs on half-spheres, spherical caps, and spherical triangles is future work, and has applications in weather prediction \cite{staniforth2012horizontal}. Other extensions include a full $hp$-finite element method on sections of a disk, which has applications in turbulent pipe flow.
%
%\noindent{\bf Acknowledgements}: We would like to thank the anonymous referees for their helpful comments. The author SO was supported in part by the Leverhulme Trust Research Project Grant RPG?2019?144 \enquote{Constructive approximation theory on and inside algebraic curves and surfaces}. The author BS was supported by the Engineering and Physical Sciences Research Council Mathematics of Planet Earth Centre for Doctoral Training at Imperial College London and the University of Reading, with grant number EP/L016613/1.

\section{P-finite element methods using sparse operators}\label{Appendix:PFEM}

\begin{figure}[t]
	\begin{subfigure}{0.3\textwidth}
	\includegraphics[scale=0.28]{solution-pfem-poisson-diskslice-alpha=0p2-beta=0p8-f=Wycosx}
        	%\label{fig:solutionblocknorms-poisson}
	\centering
	\end{subfigure}
	\begin{subfigure}{0.3\textwidth}
	\includegraphics[scale=0.3]{solution-poisson}
	\centering
	%\label{fig:solution-poisson}
	\end{subfigure}
	\begin{subfigure}{0.3\textwidth}
	\includegraphics[scale=0.3]{solution-trapezium-helmholtz-k=100-n=1500}
	%\label{fig:solution-poisson}
	\centering
	\end{subfigure}
	\centering
	\caption{Left: The computed solution to $\Delta u = f$ with zero boundary conditions with $f(x,y) = \Wiii(x,y) y \cos(x)$ in the disk-slice using the $p$-FEM approach with a single element. Centre: The computed solution to $\Delta u = f$ with zero boundary conditions with $f(x,y) = 1 + \text{erf}(5(1 - 10((x - 0.5)^2 + y^2)))$ in the half-disk. Right: The computed solution to $\Delta u + k^2 \: v \: u = f$ with zero boundary conditions with $f(x,y) = (1-x) \: x \: y \: (1- \half x - y) \: e^x$, $v(x,y) = 1 - (3(x-1)^2 + 5y^2)$ and $k = 100$. in the trapezium.}
	\centering
	\label{fig:appendixfigs}
\end{figure}

@@

>>>>

\begin{figure}[tp]
	\centering % <-- added
	\begin{subfigure}{0.5\textwidth}
		\includegraphics[scale=0.5]{sparsityoflaplacian-w11-diskslice-alpha=0p2-beta=0p8}
		\centering
		\caption{The Laplacian operator $\laplacewiii$}
	\end{subfigure}\hfil % <-- added
	\begin{subfigure}{0.5\textwidth}
		\includegraphics[scale=0.5]{sparsityofhelmholtz-diskslice-alpha=0p2-beta=0p8}
		\centering
		\caption{A variable coefficient Helmholtz operator}
	\end{subfigure}\hfil % <-- added

	\medskip
	\begin{subfigure}{0.5\textwidth}
		\includegraphics[scale=0.5]{sparsityofbiharmonic-diskslice-alpha=0p2-beta=0p8}
		\centering
		\caption{The biharmonic operator $\biharmonictwo$}
	\end{subfigure}\hfil % <-- added
    	\caption{"Spy" plots of (differential) operator matrices, showing their sparsity. For (b), the weighted variable coefficient Helmholtz operator is $\laplacewiii + k^2 \: T^{(0,0,0)\to(1,1,1)} \: V({J_x^{(0,0,0)}}^\top, {J_y^{(0,0,0)}}^\top) \: T_W^{(1,1,1)\to(0,0,0)}$ for $v(x,y) = 1 - (3(x-1)^2 + 5y^2)$ and $k = 200$.}
	\label{fig:sparsity}
\end{figure}

General linear partial differential operators with polynomial variable coefficients can be constructed by composing the sparse representations for partial derivatives, conversion between bases, and Jacobi operators. As a canonical example, we can obtain the matrix operator for the Laplacian $\Delta$, that will take us from coefficients for expansion in the weighted space
\bseqn{
	\bigWiii(x,y) = \Wiii(x,y) \: \bighdopiii(x,y)
}
to coefficients in the non-weighted space $\bighdopiii(x,y)$. Note that this construction will ensure the imposition of the Dirichlet zero boundary conditions on $\Omega$. The matrix operator for the Laplacian we denote $\laplacewiii$ acting on the coefficients vector is then given by
\bseqn{
    \laplacewiii := D_x^{(0,0,0)} \: W_x^{(1,1,1)} + T^{(0,0,1)\to(1,1)} \: D_y^{(0,0,0)} \: T_W^{(1,1,0)\to(0,0,0)} \: W_y^{(1,1,1)}.
}
Importantly, this operator will have banded-block-banded structure, and hence will be sparse, as seen in Figure \ref{fig:sparsity}.

@@

% FIGURES
\begin{figure}[t]
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[scale=0.35]{solution-poisson-diskslice-alpha=0p2-beta=0p8}
		\centering
		%\label{fig:solution-poisson}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[scale=0.45]{solutionblocknorms-poisson-diskslice-alpha=0p2-beta=0p8-N=200}
        		%\label{fig:solutionblocknorms-poisson}
	\end{subfigure}
	\caption{Left: The computed solution to $\Delta u = f$ with zero boundary conditions with $f(x,y) = 1 + \text{erf}(5(1 - 10((x - 0.5)^2 + y^2)))$. Right: The norms of each block of the computed solution of the Poisson equation with the given right hand side functions. This demonstrates algebraic convergence with the rate dictated by the decay at the corners, with spectral convergence observed when the right-hand side vanishes to all orders.}
	\centering
	\label{fig:poisson}
\end{figure}

\begin{figure}[t]
	\begin{subfigure}{0.3\textwidth}
	\includegraphics[scale=0.35]{solution-exact-poisson-diskslice-alpha=0p2-beta=0p8-u=y3expx}
	\centering
	\end{subfigure}
	\begin{subfigure}{0.3\textwidth}
	\centering
	\includegraphics[scale=0.35]{solution-exact-poisson-diskslice-alpha=0p2-beta=0p8-u=y3expx-actual}
	\centering
	\end{subfigure}
	\begin{subfigure}{0.3\textwidth}
	\includegraphics[scale=0.35]{solution-exact-poisson-diskslice-alpha=0p2-beta=0p8-u=y3expx-compare}
	\centering
	\end{subfigure}
	\centering
	\caption{The computed solution to $\Delta u = f$ with zero boundary conditions compared with the exact solution $u(x,y) = \Wiii (x,y) y^3 \exp(x)$. Left: Computed. Centre: Exact. Right: Plot of the error (colourbar is shown to demonstrate magnitude of the error is of the order $10^{-17}$)}
	\centering
	\label{fig:poissonexact}
\end{figure}

\begin{figure}[t]
	\begin{subfigure}{0.3\textwidth}
	\centering
	\includegraphics[scale=0.35]{solution-helmholtz-diskslice-alpha=0p2-beta=0p8-k=100-n=300}
	%\label{fig:solution-helmholtz}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
	\includegraphics[scale=0.45]{solutionblocknorms-helmholtz-diskslice-alpha=0p2-beta=0p8-N=196-k=20}
	\centering
        	%\label{fig:solutionblocknorms-helmholtz}
	\end{subfigure}
	\caption{Left: The computed solution to $\Delta u + k^2 \: v \: u = f$ with zero boundary conditions with $f(x,y) = x(1-x^2-y^2)e^x$, $v(x,y) = 1 - (3(x-1)^2 + 5y^2)$ and $k = 100$. Right: The norms of each block of the computed solution of the Helmholtz equation with the given right hand side functions, with $k=20$ and $v(x,y) = 1 - (3(x-1)^2 + 5y^2)$.}
	\centering
	\label{fig:helmholtz}
\end{figure}

\begin{figure}[t]
	\begin{subfigure}{0.3\textwidth}
	\centering
	\includegraphics[scale=0.35]{solution-biharmonic-diskslice-alpha=0p2-beta=0p8}
	%\label{fig:solution-biharmonic}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
	\includegraphics[scale=0.45]{solutionblocknorms-biharmonic-diskslice-alpha=0p2-beta=0p8-N=200}
	\centering
        	%\label{fig:solutionblocknorms-biharmonic}
	\end{subfigure}
	\caption{Left: The computed solution to $\Delta^2 u = f$ with zero Dirichlet and Neumann boundary conditions with $f(x,y) = 1 + \text{erf}(5(1 - 10((x - 0.5)^2 + y^2)))$. Right: The norms of each block of the computed solution of the biharmonic equation with the given right hand side functions.}
	\centering
	\label{fig:biharmonic}
\end{figure}
% END FIGURES

@@

\subsection{End-Disk-Slice}\label{section:ds:enddiskslice}

@@

In Figure \ref{fig:ds:trappfem} we see the solution to the Poisson equation with zero boundary conditions in the half-disk $\Omega$ with $(\alpha,\beta) := (0,1)$.

\subsection{Trapeziums}\label{section:ds:trapezium}

@@

In Figure \ref{fig:ds:trappfem} we see the solution to the Helmholtz equation with zero boundary conditions in the trapezium $\Omega$ with $\xi := \half$.

@@

\section{P-finite element methods using sparse operators}\label{section:ds:PFEM}

\begin{figure}[t]
	\begin{subfigure}{0.3\textwidth}
	\includegraphics[scale=0.35]{solution-pfem-poisson-diskslice-alpha=0p2-beta=0p8-f=Wycosx}
        	%\label{fig:solutionblocknorms-poisson}
	\centering
	\end{subfigure}
	\begin{subfigure}{0.3\textwidth}
	\includegraphics[scale=0.38]{solution-poisson}
	\centering
	%\label{fig:solution-poisson}
	\end{subfigure}
	\begin{subfigure}{0.3\textwidth}
	\includegraphics[scale=0.38]{solution-trapezium-helmholtz-k=100-n=1500}
	%\label{fig:solution-poisson}
	\centering
	\end{subfigure}
	\centering
	\caption{Left: The computed solution to $\Delta u = f$ with zero boundary conditions with $f(x,y) = \Wiii(x,y) y \cos(x)$ in the disk-slice using the $p$-FEM approach with a single element. Centre: The computed solution to $\Delta u = f$ with zero boundary conditions with $f(x,y) = 1 + \text{erf}(5(1 - 10((x - 0.5)^2 + y^2)))$ in the half-disk. Right: The computed solution to $\Delta u + k^2 \: v \: u = f$ with zero boundary conditions with $f(x,y) = (1-x) \: x \: y \: (1- \half x - y) \: e^x$, $v(x,y) = 1 - (3(x-1)^2 + 5y^2)$ and $k = 100$. in the trapezium.}
	\centering
	\label{fig:ds:trappfem}
\end{figure}

@@

\section{Conclusions}

In this chapter we have shown that bivariate orthogonal polynomials can lead to sparse discretizations of general linear PDEs on specific domains whose boundary is specified by an algebraic curve -- notably here the disk-slice -- with Dirichlet boundary conditions. This work extends the triangle case \cite{beuchler2006new,li2010optimal,olver2019triangle} and whole disk case \cite{} \bstodo{cite} to non-classical geometries, and forms a building block in developing an $hp-$finite element method to solve PDEs on other polygonal domains by using suitably shaped elements (for example, by dividing the disk or a section of the disk into disk-slice elements, which has applications in turbulent pipe flow \cite{}\bstodo{cite}).

We have demonstrated how one can construct the three-or-four-parameter OP families (depending on the domain) that form the basis for our sparse spectral methods, and presented a procedure, utilising the Christoffel-Darboux formula \cite[18.2.2]{DLMF}, of explicitly calculating the recurrence coefficients for the univariate OPs that are part of the construction. These coefficients contribute to calculations of the entries in the Jacobi matrices and other differential operators. Moreover, we have defined a quadrature rule that can be used for expanding functions in our OP basis and for calculating said entries of important operators. We have looked at a few mathematical examples including the Poisson, variable coefficient Helmholtz, and biharmonic equations and shown that our method performs well. Importantly, all operator matrices used are shown to be sparse, and in fact banded-block-banded in structure.

Looking ahead, this work serves as a stepping stone to constructing similar methods to solve partial differential equations on sub-domains of the $2$-sphere surface, such as spherical caps that we will discuss in the next chapter.

%, see \cite[Theorem 3.1]{olver2018orthogonal} for a similar construction of OPs on an arc in 2D, and it is clear from the construction in this paper that discretizations of spherical gradients and Laplacian's are sparse on half-spheres and other suitable sub-components of the sphere. The resulting sparsity in high-polynomial degree discretizations presents an attractive alternative to methods based on bijective mappings (e.g., \cite{DGShallowWater,FEMShallowWater,boyd2005sphere}). Constructing these sparse spectral methods for surface PDEs on half-spheres, spherical caps, and spherical triangles is future work, and has applications in weather prediction \cite{staniforth2012horizontal}. Other extensions include a full $hp$-finite element method on sections of a disk, which has applications in turbulent pipe flow.

### 2021-05-26 papers/thesis/full/ch4-spherical-caps/spherical-caps.tex
Fig sizes changed to be consistent and bigger.

What about other boundary conditions? One simple extension is the case where the value on the boundary takes that of a function depending only on $x$ and $y$, i.e. $c = c(x,y)$. In this case, the problem
\bseqn{
	\begin{cases}
    		\DeltaS u(x,y,z) + k^2 \: v(x,y,z) \; u(x,y,z) = f(x,y,z) &\quad \text{in } \Omega \\
		u(x,y,z) = c(x,y) &\quad \text{on } \partial \Omega
	\end{cases}
}
is equivalent to letting $u(x,y,z) = \tilde{u}(x,y,z)+ c(x,y)$ and solving
\bseqn{
	\begin{cases}
    		\DeltaS \tilde{u}(x,y,z) + k^2 \: v(x,y,z) \; \tilde{u}(x,y,z) = f(x,y,z) - k^2 \: v(x,y,z) \: c(x,y) - \DeltaS \: c(x,y)  \quad \text{in } \Omega \\
		\tilde{u}(x,y,z) = 0 \quad \text{on } \partial \Omega
	\end{cases}
}
for $\tilde u$. This new problem is then a zero boundary condition Helmholtz problem with right hand side 
\bseqn{
	g(x,y,z) &:= f(x,y,z) - k^2 \: v(x,y,z) \: c(x,y) - \DeltaS \: c(x,y)
}
for $(x,y,z) \in \Omega$. Notice that the spherical Laplacian applied to $c(x,y)$, expanded in the $\bigscopN^{(1)}$ basis with coefficients vector $\vec c = (c_{n,k,i})$, is just
\bseqn{
	\DeltaS \: c(x,y) = {1 \over \rho(z)^2} \sum_{n=0}^N \sum_{i=0}^1 c_{n,n,i} \: \pmpxm{\theta}{2} \ch_{n,i}(\theta) = - {1 \over \rho(z)^2} \sum_{n=0}^N \sum_{i=0}^1 n^2 \: c_{n,n,i} \: \ch_{n,i}(\theta)
}
since the coefficients $\{c_{n,k,i}\}$ for such a function are zero for $k < n$ due to the dependence on $x$ and $y$ only, which are precisely the Fourier coefficients of $c(\cos \theta, \sin \theta)$. Thus, since the function $c(x,y)$ is known, it is simple to evaluate $\pmpxm{\theta}{2} c(x,y)$ and hence one can obtain the coefficients for the expansion of $g(x,y,z)$ in the $\bigscopN^{(1)}$ basis in the usual manner.

>>>>

What about other boundary conditions? One simple extension is the case where the value on the boundary takes that of a function depending only on $x$ and $y$, i.e. $c = c(x,y)$. In this case, the problem
\bseqn{
	\begin{cases}
    		\DeltaS u(x,y,z) + k^2 \: v(x,y,z) \; u(x,y,z) = f(x,y,z) &\quad \text{in } \Omega \\
		u(x,y,z) = c(x,y) &\quad \text{on } \partial \Omega
	\end{cases}
}
is equivalent to letting $u(x,y,z) = \tilde{u}(x,y,z)+ c(x,y)$ and solving
\bseqn{
	\begin{cases}
    		\DeltaS \tilde{u}(x,y,z) + k^2 \; v(x,y,z) \tilde{u}(x,y,z) = g(x,y,z) \quad \text{in } \Omega \\
		\tilde{u}(x,y,z) = 0 \quad \text{on } \partial \Omega
	\end{cases}
}
for $\tilde u$, where 
\bseqn{
	g(x,y,z) &:= f(x,y,z) - k^2 \: v(x,y,z) \: c(x,y) - \DeltaS \: c(x,y)
}
for $(x,y,z) \in \Omega$. This new problem is then a zero boundary condition Helmholtz problem with right hand side $g$. Notice that the spherical Laplacian applied to $c(x,y)$, expanded in the $\bigscopN^{(1)}$ basis with coefficients vector $\vec c = (c_{n,k,i})$, is just
\bseqn{
	\DeltaS \: c(x,y) &= {1 \over \rho(z)^2} \pmpxm{\theta}{2} c(x,y) \\
	&= {1 \over \rho(z)^2} \sum_{n=0}^N \sum_{i=0}^1 c_{n,n,i} \: \pmpxm{\theta}{2} \ch_{n,i}(\theta) \\
	&= - {1 \over \rho(z)^2} \sum_{n=0}^N \sum_{i=0}^1 n^2 \: c_{n,n,i} \: \ch_{n,i}(\theta)
}
since the coefficients $\{c_{n,k,i}\}$ for such a function are zero for $k < n$ due to the dependence on $x$ and $y$ only, which are precisely the Fourier coefficients of $c(\cos \theta, \sin \theta)$. Thus, since the function $c(x,y)$ is known, it is simple to evaluate $\pmpxm{\theta}{2} c(x,y)$ and hence one can obtain the coefficients for the expansion of $g(x,y,z)$ in the $\bigscopN^{(1)}$ basis in the usual manner.
